Degeneracy and parameter magnitude

### 2015-03-09 Toy Example/expected value/apps/degen_magnitude.Rmd
added powers

```{r data, message=FALSE, warning=FALSE, echo=FALSE}
load("results.RData")

@@

    inner_join(ratio, res$outside[[i]] %>% ungroup()) %>%
      select(ss_ratio, near_hull) %>%
      mutate(H = H, V = V, n_param = H + V + H*V) %>%
      rbind(plot.data) -> plot.data
  }
  return(plot.data)
}

plot.dat <- lapply(res, plot_data)
names(plot.dat) <- gsub("[.]", "_", r_center)

do.call(rbind, plot.dat) %>%
  mutate(name = rownames(do.call(rbind, plot.dat))) %>%
  separate(name, into = c("multiplier", "num"), "[.]") %>% 
  mutate(multiplier = as.numeric(gsub("_", ".", multiplier))) %>%
  mutate(n_param_f = factor(n_param)) %>%
  group_by(n_param_f, multiplier) %>%
  summarise(frac_degen = sum(near_hull)/n()) -> ggvis.dat
```

@@

ggvis.subset <- reactive({
  do.call(rbind, plot.dat) %>%
    mutate(name = rownames(do.call(rbind, plot.dat))) %>%
    mutate(n_param_f = factor(n_param)) %>%
    separate(name, into = c("multiplier", "num"), "[.]") %>% 
    mutate(multiplier = as.numeric(gsub("_", ".", multiplier))) %>%
    filter(multiplier == multiplier$current) 
})

@@

```{r plots2, message=FALSE, warning=FALSE, echo=FALSE, out.height=300}

@@

## params ----------------------------------
n <- 100
r_center <- seq(0.2, 3, by = 0.2)
#r_center <- 1
r_exp <- .05

>>>>

```{r data, message=FALSE, warning=FALSE, echo=FALSE}

## params ----------------------------------
n <- 100
r_center <- seq(0.2, 3, by = 0.2)
r_exp <- .05
sliderInput("power", "Power of N:", min = 0, max = 1, value = 0, step = 0.1)

@@

    inner_join(ratio, res$outside[[i]] %>% ungroup()) %>%
      select(ss_ratio, near_hull) %>%
      mutate(H = H, V = V, n_param = H + V + H*V) %>%
      rbind(plot.data) -> plot.data
  }
  return(plot.data)
}
plot.dat <- list()
for(i in seq(0, 1, by = 0.1)) {
  load(paste0("results_", i, ".RData")) 
  plot_dat <- lapply(res, plot_data)
  names(plot_dat) <- gsub("[.]", "_", r_center)
  plot.dat[[i*10 + 1]] <- plot_dat
}

@@

ggvis.dat <- reactive({
  if(is.null(input$power)) {
    dat <- plot.dat[[1]]
  } else
    dat <- plot.dat[[input$power*10 + 1]]

  do.call(rbind, dat) %>%
    mutate(name = rownames(do.call(rbind, dat))) %>%
    separate(name, into = c("multiplier", "num"), "[.]") %>% 
    mutate(multiplier = as.numeric(gsub("_", ".", multiplier))) %>%
    mutate(n_param_f = factor(n_param)) %>%
    group_by(n_param_f, multiplier) %>%
    summarise(frac_degen = sum(near_hull)/n()) 
})

@@

```{r plots2, message=FALSE, warning=FALSE, echo=FALSE, out.height=300}
ggvis.subset <- reactive({
  if(is.null(input$power)) {
    dat <- plot.dat[[1]]
  } else
    dat <- plot.dat[[input$power*10 + 1]]

  do.call(rbind, dat) %>%
    mutate(name = rownames(do.call(rbind, dat))) %>%
    mutate(n_param_f = factor(n_param)) %>%
    separate(name, into = c("multiplier", "num"), "[.]") %>% 
    mutate(multiplier = as.numeric(gsub("_", ".", multiplier))) %>%
    filter(multiplier == multiplier$current) %>%
    return()
})

@@
